### 2020-04-21 final_report/data.tex
fill in param table

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Parameter name & Type & Domain & Description\\
		\midrule
		TODO & TODO & TODO & TODO\\
		\bottomrule
		\end{tabular}
	}
	\caption{Input parameters supplied to the MC TBR simulation.}
	\label{tbl:params}
\end{table}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{l|llll}
		\toprule
		{} & Parameter name & Type & Domain & Description\\
		\midrule
		\parbox[t]{2mm}{\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		& Breeder fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & TODO\\
		& Breeder \isotope[6]{Li} enrichment fraction & Continuous & $[0,1]$ & {}\\
		& Breeder material & Discrete & $\{\ce{Li2TiO3}, \ce{Li4SiO4}\}$ & {}\\
		& Breeder packing fraction & Continuous & $[0,1]$ & {}\\
		& Coolant fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		& Multiplier fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Multiplier material & Discrete & $\{\ce{Be}, \ce{Be12Ti}\}$ & {}\\
		& Multiplier packing fraction & Continuous & $[0,1]$ & {}\\
		& Structural fraction\textsuperscript{\textdagger} & Continuous & $[0,1]$ & {}\\
		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		& Thickness & Continuous & $[0,500]$ & {}\\
		\midrule
		\parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{First wall}}}
		& Armour fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Armour material & Discrete & $\{\text{tungsten}\}$ & {}\\
		& Coolant fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Coolant material & Discrete & $\{\ce{D2O}, \ce{H2O}, \ce{He}\}$ & {}\\
		& Structural fraction\textsuperscript{\textdaggerdbl} & Continuous & $[0,1]$ & {}\\
		& Structural material & Discrete & $\{\ce{SiC}, \text{eurofer}\}$ & {}\\
		& Thickness & Continuous & $[0,20]$ & {}\\
		\bottomrule
		\end{tabular}
	}
	\caption{Input parameters supplied to the MC TBR simulation in alphabetical
		order. Fractions marked with superscripts\textsuperscript{\textdagger
		\textdaggerdbl} are independently required to sum to one.}
	\label{tbl:params}
\end{table}
